### 2020-08-21 thesis/thesis.tex
[thesis] Cite Sangiorgi advanced book on bisim and coinduction

\vbox{\begin{verbatim}
    handle
        let fh <- do Open "praise.txt" in
        let c <- do Choice () in
        if c then do Write (fh, "Guy Fieri") else do Write (fh, "is cool");
        close fh
    with {
        return x -> [x] |
        choose () k -> return (append (k true) (k false)) |
    }
\end{verbatim}
}

@@

    \noindent
    For more detailed introduction into coinduction and other examples,
    see~\cite{jacobs-rutten, sangiorgi-intro}.

    \noindent
    TODO maybe also write coinductive proof based on two relations above?

>>>>

\vbox{\begin{verbatim}
    handle
        let fh <- do Open "praise.txt" in
        let c <- do Choice () in
        if c then do Write (fh, "Guy Fieri") else do Write (fh, "is cool");
        do Close fh
    with {
        return x -> [x] |
        Choose _ k -> return (append (k true) (k false)) |
    }
\end{verbatim}
}

@@

    \noindent
    For more detailed introduction into coinduction and other examples,
    see~\cite{jacobs-rutten, sangiorgi-intro} or for a deeper
    dive~\cite{sangiorgi-advanced}.
